InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex

\subsubsection{Image generating models}

\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month. They have two primary methods for checking if a text is AI written. Firstly linguistic analysis analyses every text for its characteristics like repetitiveness. These characteristics are different between AI and humans. Secondly the other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected. \cite{WinstonAI}

>>>>

\subsubsection{Image generating models}
The first image generating model we us is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
